---
title: "Lab 00 - Hello IDS!"
author: "Daniel Lyons "
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Evan", "Erhan", "Arran", 
           "Ross", "Daniel"),
  github_username = c("evanhealy", "ErhanHu", "ArranCuthbert", 
                      "RossAnton", "s2544544"), 
  colour = c("green", "light blue", "yellow", 
             "blue", "purple"),
  hobby = c("tennis", "reading", "football", 
            "football", "karate"),
  favourite_number = c(2, 3, 4, 5, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


bar graph with name on x-axis and number of y-axis, favourite number and colour is assigned to the names 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

Labels the axes of the graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
